Software Citation Principles

### 2016-07-23 sc-principles/software-citation-principles.tex
comments on use case 7
edits to use case 13
added some detail to use case 14

\katznote{I think we should merge this with B.1, as suggested in the google doc - the bullets are all the same}

@@

A repository that archives and/or maintains a collection of software.
The repository would like to address usage and impact of software in its holding.
Usage would aid potential users whether the software is being actively maintained or developed or has been superseded.
Both would help repository know how to direct resources, e.g., maintenance, training etc.

Requirements:
\begin{itemize}
\item Code name ideally, a unique identifier
\item Relationships to previous versions
\item Connect to repository
\item Connect to research
\end{itemize}

similar to Funder case

mineable via repository name, code name, DOI, or citation.\niemnote{complete?}

@@

>>>>

\katznote{I think we should merge this with B.1, as suggested in the google doc - the bullets are all the same}
\niemnote{the title and description are quite different---based on the description, this actually seems like 5}

@@

A repository that archives and/or maintains a collection of software.
The repository would like to address usage and impact of software in its holding.
Usage would aid potential users whether the software is being actively maintained or developed or has been superseded.
Both would help repository know how to direct resources, e.g., maintenance, training etc.
This is similar to the case of a funder wanting to know the impact of funded work.

Requirements:
\begin{itemize}
\item Code name, or a unique identifier
\item Relationships to previous versions
\item Connect to repository
\item Connect to research
\end{itemize}

@@

This use case is similar to ``Repository showing scientific impact of holdings'',
where a funder wants to find out the use and impact and software that they
supported.
